A game theoretic model of the behavioural gaming that takes place at the EMS - ED interface

### 2021-11-05 sections/queueing_model/main.tex
Apply changes to queueing sections

\section{A queueing model with 2 consecutive buffer centres}\label{sec:queueing_model}
% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queuing model that consists of two waiting spaces, one for each type
of individual.

The model consists of two types of individuals; type 1 and type 2.
Type 1 individuals arrive instantly at waiting zone 1 and wait to receive their 
service. 
Type 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed only when the number of 
individuals in waiting zone 1 \textbf{and} in service is less than a 
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all 
second type individuals that arrive will stay 
\textit{``blocked''} in waiting zone 2 until the number of people in 
the next queue and in service falls below \(T\). 
This is shown diagrammatically in figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

@@

Under the assumption that all rates (arrival and service) are Markovian the
queuing system corresponds to a Markov chain~\cite{kemeny1976markov}.
The states of the Markov chain are denoted by \((u,v)\) where:

@@

Note that \(\Lambda\) here denotes the overall arrival rate in the model by both 
types of individuals (i.e. \(\Lambda = \lambda_1 + \lambda_2\)). 
A visualisation of how the transition rates relate to the states of the model 
can be seen in the general Markov chain model shown in figure 
\ref{fig:general_markov_model}.

@@

Using vector \(\pi\) there are numerous performance measures of the model that 
can be calculated. 
The following equations utilise \(\pi\) to get performance measures on the 
average number of people at certain sets of state.

>>>>

\section{A queueing model with 2 consecutive buffer centres}\label{sec:queueing_model}
% TODO: If this is to be one paper maybe the first two paragraphs do not need to
% include so much details or even better omit some of the details in the game
% overview section.
In this section, a more in-depth explanation of the queueing model shown in 
figure \ref{fig:diagram_of_queueing_system} will be given.
This is a queueing model that consists of two waiting zones, one for each type
of individual.

The model consists of two types of individuals; type 1 and type 2.
Type 1 individuals arrive instantly at waiting zone 1 and wait to receive their 
service. 
Type 2 individuals arrive at waiting zone 2 and wait there until they are 
allowed to move to waiting zone 1. 
They are allowed to proceed only when the number of 
individuals in waiting zone 1 \textbf{and} in service is less than a 
pre-determined threshold \(T\).
When the number of individuals is equal to or exceeds this threshold, all 
second type individuals that arrive will stay 
\textit{blocked} in waiting zone 2 until the number of people in 
the next queue and in service falls below \(T\). 
This is shown diagrammatically in Figure \ref{fig:diagram_of_queueing_system}.
The parameters of the described queueing model are:

@@

Under the assumption that all rates (arrival and service) are Markovian the
queueing system corresponds to a Markov chain~\cite{kemeny1976markov}.
The states of the Markov chain are denoted by \((u,v)\) where:

@@

Note that \(\Lambda\) here denotes the overall arrival rate in the model by both 
types of individuals (i.e. \(\Lambda = \lambda_1 + \lambda_2\)). 
A visualisation of how the transition rates relate to the states of the model 
can be seen in the general Markov chain model shown in Figure 
\ref{fig:general_markov_model}.

@@

Using vector \(\pi\) there are numerous performance measures of the model that 
can be calculated. 
The following equations utilise \(\pi\) to get performance measures on the 
average number of people at certain sets of state:

### 2021-11-05 sections/queueing_model/proportion_within_target/main.tex
Apply changes to queueing sections

Another performance measure that is taken into consideration is the proportion 
of individuals whose waiting and service times are within a specified 
time target \(t\).
Similar to section \ref{sec:waiting_time} three formulas are needed for this 
performance measure.

@@

Refer to appendix \ref{sec:appendix_mean_proportion} for a more in-depth 
explanation of the origins of equations 
(\ref{eq:proportion_within_target_type_1}) - 
(\ref{eq:proportion_within_target_type_2_from_state}).

>>>>

Another performance measure that is taken into consideration is the proportion 
of individuals whose waiting and service times are within a specified 
time target \(t\).
Similar to section \ref{sec:waiting_time}, three formulas are needed for this 
performance measure.

@@

Please refer to appendix \ref{sec:appendix_mean_proportion} for a more in-depth 
explanation of the origins of equations 
(\ref{eq:proportion_within_target_type_1}) - 
(\ref{eq:proportion_within_target_type_2_from_state}).

### 2021-11-05 sections/queueing_model/waiting_time/main.tex
Restructure queueing model section
Remove performance measures subsection and change "waiting time",
"blocking time" and "proportion of inds" from subsubsections into
subsections. Also add example subsubsections
Write appendix chapter for DES model
Section: A queueing model with 2 consecutive buffer centres (#6)
* Add bibliography entry

* Write details of the Markov-chain model

- Define the model
- Define state space
- Define transition matrix and state-mapping function

* Add general Markov-chain picture

* Update known.py

* Add .pdf file to GitHub repo

* Create subsections/ subdirectory

\subsubsection{Waiting time} \label{sec:waiting_time}

Waiting time is the amount of time that individuals from either type wait in 
waiting zone 1 so that they can receive their service. 
For a given set of parameters there are three different performance measures 
around the mean waiting time that can be calculated; the mean waiting time of
type 1 individuals:

@@

Figures \ref{fig:markov_vs_des_waiting_time_comparison_1},
\ref{fig:markov_vs_des_waiting_time_comparison_2} and
\ref{fig:markov_vs_des_waiting_time_comparison_overall} show a comparison 
between the calculated mean waiting time using Markov chains and the simulated 
waiting time using discrete event simulation over a range of values of 
\(\lambda_2\).
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.

>>>>

\subsection{Waiting time} \label{sec:waiting_time}

Waiting time is the amount of time that individuals from either type wait in 
waiting zone 1 so that they can receive their service. 
For a given set of parameters there are three different performance measures 
around the mean waiting time that can be calculated. The mean waiting time of
type 1 individuals:

@@

Figures \ref{fig:markov_vs_des_waiting_time_comparison_1},
\ref{fig:markov_vs_des_waiting_time_comparison_2} and
\ref{fig:markov_vs_des_waiting_time_comparison_overall} show a comparison 
between the calculated mean waiting time using Markov chains and the simulated 
waiting time using discrete event simulation over a range of values of 
\(\lambda_2\) (details of the discrete event simulation model are given in 
appendix~\ref{sec:appendix_des}).
The simulation was ran 100 times and the recorded mean waiting time at each 
iteration is used to populate the violin plots.
For all three plots the waiting times generated by the simulation match the
ones generated by the Markov chains model.
